### 2022-10-29 dissertation/chapters/04-hyper-heuristics.tex
✨ (chapter4): Small fixes

      \item \textbf{Section \ref{sec:hh:classification}} provides a detailed discussion on the classification and types of \acp{HH}. Distinction is made between online and offline learning mechanisms. Discussions follow on selection and generation \acp{HH}, and constructive and generative mechanisms.

      \item \textbf{Section \ref{sec:hh:summary}} provides a summary of the chapter.
\end{itemize}

@@

Selection \acp{HH} consists of two components, including a low-level \index{heuristic}heuristic selection strategy and a move acceptance strategy. Low-level \index{heuristic}heuristic selection can be done in a simple, \textit{non-adaptive} way. No learning is involved in these approaches. For non-adaptive techniques, heuristic selection is based on a predefined heuristic ordering that is generated either randomly or in a ordered cycle that is repeated throughout the optimisation process~\cite{ref:cowling:2000}. As an alternative, heuristic selection may incorporate an \textit{adaptive} (\index{online learning)}\textit{online learning}) mechanism, based on the probabilistic weighting of the low-level heuristics~\cite{ref:burke:2003} or some type of performance statistics~\cite{ref:cowling:2000}.

@@

\section{Summary}
\label{sec:hh:summary}

>>>>

      \item \textbf{Section \ref{sec:hh:classification}} provides a detailed discussion on the classification and types of \acp{HH}. Distinction is made between online and offline learning mechanisms. Discussions follow on selection and generation \acp{HH}, and construction and perturbation mechanisms.

      \item \textbf{Section \ref{sec:hh:summary}} provides a brief summary of the chapter.
\end{itemize}

@@

Selection \acp{HH} consists of two components, including a low-level \index{heuristic}heuristic selection strategy and a move acceptance strategy. Low-level \index{heuristic}heuristic selection can be done in a simple, \textit{non-adaptive} way. No learning is involved in these approaches. For non-adaptive techniques, heuristic selection is based on a predefined heuristic ordering that is generated either randomly or in a ordered cycle that is repeated throughout the optimisation process~\cite{ref:cowling:2000}. As an alternative, heuristic selection may incorporate an \textit{adaptive} (\index{online learning}\textit{online learning}) mechanism, based on the probabilistic weighting of the low-level heuristics~\cite{ref:burke:2003} or some type of performance statistics~\cite{ref:cowling:2000}.

@@

\section{Summary}\label{sec:hh:summary}
